smooth-sea

### 2018-06-03 dashboard/index.rmd
forgot the personal page link on the manuscript md

---
output: 
  flexdashboard::flex_dashboard:
    navbar:
       - {title: "hesscl.com", href: "http://hesscl.com", align: right}
       - {title: "Project Home", icon: "fa-home", href: "http://hesscl.com/smooth-sea/index.html", align: left} 
    orientation: columns
    theme: bootstrap
    logo: "../logo.svg"
    source_code: "https://github.com/hesscl/smooth-sea"
---

>>>>

---
title: "smooth-sea"
output: 
  flexdashboard::flex_dashboard:
    navbar:
       - {title: "hesscl.com", href: "http://hesscl.com", align: right}
       - {title: "Project Home", icon: "fa-home", href: "http://hesscl.com/smooth-sea/index.html", align: right} 
    orientation: columns
    theme: bootstrap
    logo: "../logo.svg"
    source_code: "https://github.com/hesscl/smooth-sea/"
---
